Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data

### 2012-02-16 presentations/extended_source_search/lande_ext_src_search_fermi_lunch/lande_ext_src_search_fermi_lunch.tex
improve

\begin{frame}{2 Extended SNRs}
  \begin{columns}
    \column{.50\textwidth} 
    Puppis A

    \includegraphics[scale=0.40]{plots/source_Puppis_A_color.pdf}

    \begin{itemize}
      \item X-ray contours
      \item Mid-aged SNR
      \item Not observed to directly interact with molecular
        clouds
      \end{itemize}

    \column{.50\textwidth} 
    $\gamma$-Cygni

    \includegraphics[scale=0.40]{plots/source_Gamma_Cygni_color.pdf}

@@

\begin{frame}{Fig. 14: SED of SNRs}
  \includegraphics[scale=0.5]{plots/snr_seds_color.pdf}
\end{frame}

@@

\begin{frame}{2 More PWN Candidate}

  \begin{columns}
    \column{.45\textwidth}

2FGL\,J1632.4$-$4753c

    \includegraphics[scale=0.3]{plots/source_HESS_J1632-478_color.pdf}

    \begin{itemize}
      \item Coincident with HESS\,J1632-478

      \item  {\em XMM-Newton} point-like + extended emission
      \item (but no pulsations)
      \item PWN Candidate
    \end{itemize}

    \column{.60\textwidth}

    2FGL\,J1837.3$-$0700c

    \includegraphics[scale=0.3]{plots/source_HESS_J1837-069_color.pdf}

    \begin{itemize}
      \item Coincident with HESS\,J1837-069
      \item + X-ray pulsar PSR\,J1838$-$0655 
      \item + $\sim 2'$ X-ray PWN 
      \item PWN candidate
      \item Second X-ray PSR + PWN candidate in region
        (but no pulsations)
    \end{itemize}
  \end{columns}
\end{frame}

@@

\begin{frame}{Fig. 20: RX J1713.7$-$3946}
  \includegraphics[scale=0.5]{plots/source_RX_J1713_7-3946_color.pdf}
\end{frame}

>>>>

\begin{frame}{Fig 13: Puppis A}

  \begin{columns}
    \column{.50\textwidth} 
    \includegraphics[scale=0.50]{plots/source_Puppis_A_color.pdf}

    \column{.50\textwidth} 
    \begin{itemize}
      \item X-ray contours
      \item Mid-aged SNR
      \item Not observed to directly interact with molecular
        clouds
      \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Fig 22: $\gamma$-Cygni}
  \begin{columns}

    \column{.50\textwidth} 
    \includegraphics[scale=0.50]{plots/source_Gamma_Cygni_color.pdf}

    \column{.50\textwidth}

@@

\begin{frame}{Fig. 14: SED of SNRs}
  \includegraphics[scale=0.65]{plots/snr_seds_color.pdf}
\end{frame}

@@

\begin{frame}{Fig 19: 2FGL\,J1632.4$-$4753c }
  \begin{columns}
    \column{.6\textwidth} 
    \includegraphics[scale=0.5]{plots/source_HESS_J1632-478_color.pdf}
    \column{.4\textwidth}
    \begin{itemize}
      \item Coincident with HESS\,J1632-478

      \item  {\em XMM-Newton} point-like + extended emission
      \item (but no pulsations)
      \item PWN Candidate
    \end{itemize}
    \end{columns}
    \end{frame}

    \begin{frame}{Fig 21: 2FGL\,J1837.3$-$0700c}
    \begin{columns}
    \column{.60\textwidth} 
    \includegraphics[scale=0.5]{plots/source_HESS_J1837-069_color.pdf}
    \column{.40\textwidth} 
    \begin{itemize}
      \item Coincident with HESS\,J1837-069
      \item + X-ray pulsar PSR\,J1838$-$0655 
      \item + $\sim 2'$ X-ray PWN 
      \item PWN candidate
      \item Second X-ray PSR + PWN candidate in region
        (but no pulsations)
    \end{itemize}
  \end{columns}
\end{frame}

@@

\begin{frame}{Fig. 20: RX J1713.7$-$3946}
  \includegraphics[scale=0.65]{plots/source_RX_J1713_7-3946_color.pdf}

  Beautiful GeV Image for E$>$10 GeV!
\end{frame}
